---
title: "R Notebook"
output: html_notebook
---


# 8.15 Exercises
```{r echo=TRUE}
install.packages("dslabs")
install.packages("ggplot2")
install.packages("dplyr")
library(dplyr)
library(ggplot2)
library(dslabs)
data(heights)
data(murders)
```

1. With **ggplot2** plots can be saved as objects. For example we can associate a dataset with a plot object like this
```{r}
p <- ggplot(data = murders)
```
Because `data` is the first argument we don’t need to spell it out
```{r}
p <- ggplot(murders)
```
and we can also use the pipe:
```{r}
p <- murders %>% ggplot()
```


What is class of the object `p`?
```{r}
class(p)
##ggplot
```





2. Remember that to print an object you can use the command `print` or simply type the object. For example
```{r}
x <- 2
x
print(x)
```

Print the object `p` defined in exercise one and describe what you see.
```{r}
print(p)
##B. A blank slate plot
```



3. Using the pipe `%>%`, create an object `p` but this time associated with the `heights` dataset instead of the `murders` dataset.
```{r}
p <- heights %>% ggplot()
```



4. What is the class of the object `p` you have just created?
```{r}
class(p)
## ggplot
```



5. Now we are going to add a layers and the corresponding aesthetic mappings. 
For the murders data we plotted total murders versus population sizes. Explore the `murders` data frame to remind yourself what are the names for these two variables and select the correct answer. Hint: Look at `?murders`.
```{r}
?murders
##C. `total` and `population`.
```



6. To create the scatter plot we add a layer with `geom_point`. The aesthetic mappings require us to define the x-axis and y-axis variables respectively. So the code looks like this:
```{r}
murders %>% ggplot(aes(x = , y = )) +
  geom_point()
```
except we have to define the two variables `x` and `y`. Fill this out with the correct variable names.
```{r}
murders %>% ggplot(aes(x = population, y = total)) + geom_point()
```



7. Note that if we don’t use argument names, we can obtain the same plot by making sure we enter the variable names in the right order like this:
```{r}
murders %>% ggplot(aes(population, total)) +
  geom_point()
```

Remake the plot but now with total in the x-axis and population in the y-axis.
```{r}
murders %>% ggplot(aes(total, population)) + geom_point()
```



8. If instead of points we want to add text, we can use the `geom_text()` or `geom_label()` geometries. The following code
```{r}
murders %>% ggplot(aes(population, total)) +
  geom_label()
```
will give us the error message: 
`Error: geom_label requires the following missing aesthetics: label`
Why this?
```{r}
#A. We need to map a character to each point through the label argument in aes.
```



9. Rewrite the code above to abbreviation as the label through `aes`
```{r}
murders %>% ggplot(aes(population, total, label = abb)) +
  geom_label()
```



10. Change the color of the labels through blue. How will we do this?
```{r}
#D. Because we want all colors to be blue, we do not need to map colors, just use the color argument in geom_label
```



11. Rewrite the code above to make the labels blue.
```{r}
murders %>% ggplot(aes(population, total, label = abb)) +
  geom_label(color = "blue")
```



12. Now suppose we want to use color to represent the different regions. In this case which of the following is most appropriate:
```{r}
#B. Because each label needs a different color we map the colors through the color argument of aes .
```


13. Rewrite the code above to make the labels’ color be determined by the state’s region.
```{r}
murders %>% ggplot(aes(population, total, label = abb, col = region)) + geom_label()
```



14. Now we are going to change the x-axis to a log scale to account for the fact the distribution of population is skewed. Let’s start by define an object `p` holding the plot we have made up to now
```{r}
p <- murders %>% 
  ggplot(aes(population, total, label = abb, color = region)) +
  geom_label() 
```
To change the y-axis to a log scale we learned about the `scale_x_log10()` function. Add this layer to the object p to change the scale and render the plot

```{r}
p + scale_x_log10()
```


15. Repeat the previous exercise but now change both axes to be in the log scale.
```{r}
p + scale_x_log10() + scale_y_log10()
```



16. Now edit the code above to add the title “Gun murder data” to the plot. Hint: use the `ggtitle` function.
```{r}
p + scale_x_log10() + scale_y_log10() + ggtitle("Gun murder data")
```

