---
title: "R Notebook"
output: html_notebook
---

# Chapter 14. Random Variables

## 14.1 Random Variables
:실행할 때마다 다른 값이 나오는 변수

Here `X` is a random variable: every time we select a new bead the outcome changes randomly. See below:
```{r}
beads <- rep( c("red", "blue"), times = c(2,3))
X <- ifelse(sample(beads, 1) == "blue", 1, 0)

ifelse(sample(beads, 1) == "blue", 1, 0)
ifelse(sample(beads, 1) == "blue", 1, 0)
ifelse(sample(beads, 1) == "blue", 1, 0)
```


## 14.2 Sampling models

[urn:individuals assigned] ->(draw)-> Random

Because we know the proportions of 1s and -1s, we can generate the draws with one line of code, without defining `color`:
```{r}
n <- 1000
X <- sample(c(-1,1), n, replace = TRUE, prob=c(9/19, 10/19))
```
We call this a **sampling model** since we are modeling the random behavior of roulette with the sampling of draws from an urn. The total winnings **S** is simply the sum of these 1,000 independent draws:
```{r}
X <- sample(c(-1,1), n, replace = TRUE, prob=c(9/19, 10/19))
S <- sum(X)
S
```

## 14.3 The probability distribution of random variable
S <- random variable
F(a) = Pr(S<=a) <- random variable's distribution function
mean(S) <- expected value
sd(S) <- standard error

binominal distribution: 이항분포(일정한 확률 p를 가진 독립시행을 n번 반복했을때의 확률분포)
**B(n,p), n번 중 r번 실행될 확률: P(X=r)=nCr*p^r*(1-p)^(n-r)**
**이항분포는 discrete하다!!**

`pbinom` : 이항분포에 대하여 p(x<=a) 확률 계산
pbinom(a, size=n, prob=p)
#> p(x<=a)

`dbinom` : 이항분포에 대하여 P(x)의 값
dbinom(x, size, prob)



S is random variable.
```{r}
n <- 1000
B <- 10000
roulette_winnings <- function(n){
  X <- sample(c(-1,1), n, replace = TRUE, prob=c(9/19, 10/19))
  sum(X)
}
S <- replicate(B, roulette_winnings(n))

```

Now we can ask the following: in our simulations, how often did we get sums less than or equal to a?
```{r}
mean(S <= a)
```
This will be a very good approximation of F(a) and we can easily answer the casino’s question: how likely is it that we will lose money? We can see it is quite low:
```{r}
mean(S<0)
```


Specifically, in our example above, we can show that (S+n)/2 follow a binomial distribution.

We can use the function `dbinom` and `pbinom` to compute the probabilities exactly. For example, to compute Pr(S<0), we note that:
Pr(S<0) = Pr((S+n)/2 < (0+n)/2)
and we can use the `pbinom` to compute Pr(S<=0)
```{r}
n <- 1000
pbinom(n/2, size = n, prob = 10/19)
```

Because this is a discete probability function, to get Pr(S<0) rather than Pr(S<=0), we write:
```{r}
pbinom(n/2-1, size = n, prob = 10/19)
```



## 14.4 Distributions versus probability distributions

1. distribution function
2. drawing from urn with number
3. Monte - Carloe
#1. list of number? > 2,3
#2. 1 is theorical and 3 don't involve urn


## 14.5 Notation for random varibles

X(미래의 예측, random variable) < x(실제 측정값)


## 14.6 The expected value and standard error

E[X] : expected value of random value X
expected value : ap + b(1-p)/ ab는 결과, p와 1-p는 각 결과의 probability

expected value of a random variable defined by one draw is the average of the numbers in the urn

SE[X]: standard error: size of the variation around the expected value.
**(number of draws)^1/2 * standard deviation of the number in the urn**
**standard deviation:|b-a|*(p(1-p))^1/2**


#### 14.6.1 Population SD versus the sample SD
The standard deviation of a list `x` (below we use heights as an example) is defined as the square root of the average of the squared differences:
```{r}
install.packages("dslabs")
library(dslabs)
x <- heights$height
m <- mean(x)
s <- sqrt(mean((x-m)^2))
```
However, be aware that the sd function returns a slightly different result:
```{r}
identical(s, sd(x))
s - sd(x)
```

(x-m)^2의 평균 구할 때 원래대로라면 전체합을 n으로 나눠야되는데 sd(x)는 n-1로 나눔. 그래서 sd(x)대신 정석을 써야되는데 n의 값이 충분히 크면 그게 그거므로 sd(x)써도 됨.


## 14.7 Central Limit Theorem
CLT : number or drawn의 값이 크면 probability distribution of the sum of the independent draws is approximately normal
-> Monte Carlo대신 E[X]와 SE[X]로 값 계산 가능

We previously ran this Monte Carlo simulation:
```{r}
n <- 1000
B <- 10000
roulette_winnings <- function(n){
  X <- sample(c(-1,1), n, replace = TRUE, prob=c(9/19, 10/19))
  sum(X)
}
S <- replicate(B, roulette_winnings(n))
```

The Central Limit Theorem (CLT) tells us that the sum S is approximated by a normal distribution. Using the formulas above, we know that the expected value and standard error are:
```{r}
n * (20-18)/38 
sqrt(n) * 2 * sqrt(90)/19 
```

The theoretical values above match those obtained with the Monte Carlo simulation:
```{r}
mean(S)
sd(S)
```
Using the CLT, we can skip the Monte Carlo simulation and instead compute the probability of the casino losing money using this approximation, which is also in very good agreement with our Monte Carlo result:
```{r}
mu <- n * (20-18)/38
se <-  sqrt(n) * 2 * sqrt(90)/19 
pnorm(0, mu, se)
mean(S < 0)
```


#### 14.7.1 How large is large in the Central Limit THeorem?
보통 30
근데 success의 probability가 매우 낮을때는 아무리 숫자가 커도 normal distribution과 거리가 멈 오히려 **possion distribution**이 더욱 적절

`dpois`, `ppois`, `rpois`


## 14.8 Statistical properties of averages
1. The expected value of the sum of random variables is the sum of each random variable’s expected value.
E[X1 + X2 + X3 ...] = E[X1] + E[X2]..
If the X are independent draws from the urn, then they all have the same expected value. Let’s call it μ and thus:
E[X1 + X2 .. +  Xn] = nμ

2. The expected value of a non-random constant times a random variable is the non-random constant times the expected value of a random variable.
E[aX] = a * E[X]
E[(X1 + X2 .. +  Xn)/n] = E[(X1 + X2 .. +  Xn)]/n = nμ/n = μ

3. SE[X1 + X2 + .. +Xn] = (SE[X1]^2 + ..SE[Xn]^2)^1/2

4. SE[aX] = a*SE[X]

6. X is normally distribiuted random variable
aX + B is normally distributed random variable, that multiplying by a then shifting the center by b.


## 14.9 Law of large numbers
n이 커지면 standard error는 0에 가까워지고 average of draw는 urn의 average에 가까워짐.


#### 14.9.1 Misinterpreting law of average
law of average는 n의 숫자가 클때만 적용되고 각각의 시행은 독립이므로 앞의 결과에 영향을 받지 않는다.


## 14.10 Exercises
1.  In American Roulette you can also bet on green. There are 18 reds, 18 blacks and 2 greens (0 and 00). What are the chances the green comes out?
```{r}
2/(18+18+2)
```

2. The payout for winning on green is $17 dollars. This means that if you bet a dollar and it lands on green, you get $17. Create a sampling model using sample to simulate the random variable X for your winnings. Hint: see the example below for how it should look like when betting on red.
```{r}
X <- sample(c(17, -1), prob = c(2/38,36/38))
```

3. Compute the expected value of X
```{r}
17*2/38 -36/38
```

4. Compute the standard error of X
```{r}
18*sqrt((2/38)*(36/38))
```

5.  Now create a random variable S that is the sum of your winnings after betting on green 1000 times. Hint: change the argument `size` and `replace` in your answer to question 2. Start your code by setting the seed to 1 with `set.seed(1)`.
```{r}
set.seed(1)
sample(c(17, -1), prob = c(2/38,36/38), 1000, replace = TRUE)

set.seed(1)
results <- sample(c(17, -1), prob = c(2/38,36/38), 1000, replace = TRUE)
S <- sum(results)
```

6. What is the expected value of S?
```{r}
1000*((17*2/38)-(36/38))
```

7. What is the standard error of S?
```{r}
sqrt(1000)*18*sqrt((2/38)*(36/38))
```

8. What is the probability that you end up winning money? Hint: use the CLT
```{r}
1 - pnorm(0, -52.63, 127.10)
```

9. Create a Monte Carlo simulation that generates 1,000 outcomes of S. Compute the average and standard deviation of the resulting list to confirm the results of 6 and 7. Start your code by setting the seed to 1 with set.seed(1)
```{r}
B <- 1000
n <- 1000  

results <- replicate(B, sum(sample(c(17, -1), n, prob = c(2/38,36/38), replace = TRUE)))
```

10. Now check your answer to 8 using the Monte Carlo result.
```{r}
mean(results>0)
#두 값이 거의 일치한다.
```

11. The Monte Carlo result and the CLT approximation are close, but not that close. What could account for this?

**C. the difference is within rounding error.**

12. Now create a random variable Y that is your average winnings per beet after playing off your winnings after betting on green 1000 times.
```{r}
my_function <- function(n){
  X <- sample(c(17, -1), n, prob = c(1/19, 18/19), replace = TRUE)
  mean(X == 17)
}
my_function(n)
```

13. What is the expected value of Y?
```{r}

```

