---
title: "R Notebook"
output: html_notebook
---
# Chapter 4 Programming basics
in this section, we introduce three key programming concepts: **conditional expressions**, **for-loops** and **functions**. 


#### 4.1 Conditional expressions
hey are used for what is called **flow control**. The most common conditional expression is the if-else statement.

Here is a very simple example showing the general structure of an if-else statement. The basic idea is to print the reciprocal of `a` unless `a` is 0:
```{r}
a <- 0

if(a!=0){print(1/a)}else{print("No reciprocal for 0")}

#**if, else 서로 띄어쓰면 error뜸**
```
Let’s look at one more example using the US murders data frame:
```{r}
install.packages("dslabs")
library(dslabs)
data(murders)
murder_rate <- murders$total / murders$population*100000
```
Here is a very simple example that tells us which states, if any, have a murder rate lower than 0.5 per 100,000. The if statement protects us from the case in which no state satisfies the condition.
```{r}
ind <- which.min(murder_rate)

if(murder_rate[ind] < 0.5){
  print(murders$state[ind]) 
} else{
  print("No state has murder rate that low")
}
```
If we try it again with a rate of 0.25, we get a different answer:
```{r}
if(murder_rate[ind] < 0.25){
  print(murders$state[ind]) 
} else{
  print("No state has a murder rate that low.")
}
```
A related function that is very useful is `ifelse`. This function takes three arguments: a logical and two possible answers. If the logical is `TRUE`, the value in the second argument is returned and if `FALSE`, the value in the third argument is returned. Here is an example:
```{r}
a <- 0
ifelse(a > 0, 1/a, NA)
```
The function is particularly useful because it works on vectors. It examines each entry of the logical vector and returns elements from the vector provided in the second argument, if the entry is `TRUE`, or elements from the vector provided in the third argument, if the entry is `FALSE`.
```{r}
a <- c(0,1,2,-4,5)
result <- ifelse(a > 0, 1/a, NA)
result
```
Here is an example of how this function can be readily used to replace all the missing values in a vector with zeros:
```{r}
data(na_example)
no_nas <- ifelse(is.na(na_example), 0, na_example) 
sum(is.na(no_nas))
```
Two other useful functions are `any` and `all`. The `any` function takes a vector of logicals and returns `TRUE` if any of the entries is `TRUE`. The `all` function takes a vector of logicals and returns `TRUE` if all of the entries are TRUE. Here is an example:
```{r}
z <- c(TRUE, TRUE, FALSE)
any(z)
all(z)
```

#### 4.2 Defining functions
We can compute the average of a vector `x` using the `sum` and `length` functions: `sum(x)/length(x)`. Because we do this repeatedly, it is much more efficient to write a function that performs this operation. This particular operation is so common that someone already wrote the `mean` function and it is included in base R. However, you will encounter situations in which the function does not already exist, so R permits you to write your own. A simple version of a function that computes the average can be defined like this:
```{r}
avg <- function(x){
  s <- sum(x)
  n <- length(x)
  s/n
}
```
Now `avg` is a function that computes the mean:
```{r}
x <- 1:100
identical(mean(x), avg(x))
```
Notice that variables defined inside a function are not saved in the workspace. So while we use `s` and `n` when we call `avg`, the values are created and changed only during the call. Here is an illustrative example:
```{r}
s <- 3
avg(1:10)
s
```
Note how `s` is still 3 after we call `avg`.

In general, functions are objects, so we assign them to variable names with <-. The function function tells R you are about to define a function. The general form of a function definition looks like this:
```{r}
my_function <- function(VARIABLE_NAME){
  perform operations on VARIABLE_NAME and calculate VALUE
  VALUE}
```
The functions you define can have multiple arguments as well as default values. For example, we can define a function that computes either the arithmetic or geometric average depending on a user defined variable like this:
```{r}
avg <- function(x, arithmetic = TRUE){
  n <- length(x)
  ifelse(arithmetic, sum(x)/n, prod(x)^(1/n))
}
```


#### 4.3 Namespaces

In fact, you have already encountered this becuase both dplyr and the R-base stats package define a filter function. There are five other examples in dplyr. We know this becasue when we first load dplyr we see the following message:

The following objects are masked from ‘package:stats’:

    filter, lag

The following objects are masked from ‘package:base’:

    intersect, setdiff, setequal, union
```{r}
install.packages("dplyr")

```
So what does R do when we type `filter`? Does it use the `dplyr` function or the `stats` function? From our previous work we know it uses the `dplyr` one. But what if we want to use the `stats` version?

These function live in different `namespaces`. R will follow a certain order when searching for a function in these namespaces. You can see the order by typing:
```{r}
search()
```
The first entry in this list is the global environment which includes all the objects you define.

So what if we want to use the `stat`s filter instead of the `dplyr` filter but `dplyr` appears first in the search list? You can force the use of a specific name space by using double colons `(::)` like this:
```{r}
stats::filter
```
If we want to be absolutely sure we use the `dplyr filter` we can use
```{r}
dplyr::filter
```
Also note that if we want to use a function in a package without loading the entire package, we can use the double colon as well.


#### 3.3 For-loops
The formula for the sum of the series  
1+2+⋯+n is  n(n+1)/2. What if we weren’t sure that was the right function? How could we check? Using what we learned about functions we can create one that computes the  
Sn
:
```{r}
compute_s_n <- function(n){
  x <- 1:n
  sum(x)
}
```
How can we compute  Sn for various values of  
n, say  n=1,…,25? 
Do we write 25 lines of code calling `compute_s_n?` No, that is what for-loops are for in programming. In this case, we are performing exactly the same task over and over, and the only thing that is changing is the value of  n. 
For-loops let us define the range that our variable takes (in our example  
n=1,…,10), then change the value and evaluate expression as you loop.

Perhaps the simplest example of a for-loop is this useless piece of code:
```{r}
for(i in 1:5){
  print(i)
}
```
Here is the for-loop we would write for our  Sn example:
```{r}
m <- 25
s_n <- vector(length = m)
for(n in 1:m){
  s_n[n] <- compute_s_n(n)
}
```
In each iteration  
n=1,  n=2, etc…, we compute  Sn and store it in the  nth entry of s_n.

Now we can create a plot to search for a pattern:
```{r}
n <- 1:m
plot(n, s_n)
```
If you noticed that it appears to be a quadratic, you are on the right track because the formula is  
n(n+1)/2, which we can confirm with a table:
```{r}
head(data.frame(s_n = s_n, formula = n*(n+1)/2))
```
We can also overlay the two results by using the function `lines` to draw a line over the previously plotted points:
```{r}
plot(n, s_n)
lines(n, n*(n+1)/2)
```



#### 4.5 Vectorizatin and functionals
Although for-loops are an important concept to understand, in R we rarely use them. As you learn more R, you will realize that vectorization is preferred over for-loops since it results in shorter and clearer code. We already saw examples in the Vector Arithmetic Section. A vectorized function is a function that will apply the same operation on each of the vectors.
```{r}
x <- 1:10
sqrt(x)

y <- 1:10
x*y
```

To make this calculation, there is no need for for-loops. However, not all functions work this way. For instance, the function we just wrote, `compute_s_n`, does not work element-wise since it is expecting a scalar. This piece of code does not run the function on each entry of n:
```{r}
n <- 1:25
compute_s_n(n)
```
_Functionals_ are functions that help us apply the same function to each entry in a vector, matrix, data frame or list. Here we cover the functional that operates on numeric, logical and character vectors: `sapply`.

The function `sapply` permits us to perform element-wise operations on any function. Here is how it works:
```{r}
x <- 1:10
sapply(x, sqrt)
```
Each element of `x` is passed on to the function `sqrt` and the result is returned. These results are concatenated. In this case, the result is a vector of the same length as the original `x`. This implies that the for-loop above can be written as follows:
```{r}
n <- 1:25
s_n <- sapply(n, compute_s_n)
plot(n, s_n)
```
Other functionals are `apply`, `lapply`, `tapply`, `mapply`, `vapply`, and `replicate`. We moslty use sapply, apply, and replicate in this book, but we recommend familiarizing yourselves with the others as they can be very useful.




#### 3.6 Exercises
1. What will this conditional expression return?
```{r}
x <- c(1,2,-3,4)

if(all(x>0)){
  print("All Postives")
} else{
  print("Not all positives")
}
```
2. Which of the following expressions is always FALSE when at least one entry of a logical vector x is TRUE?
```{r}
#D
```

3. The function `nchar` tells you how many characters long a character vector is.

Write a line of code that assigns to the object `new_names` the state abbreviation when the state name is longer than 8 characters.
```{r}
name_1 <- nchar(murders$state)
name_1
x <- 1:57
name_1[x]
new_names <- for(x in 1:57){if(name_1[x] > 8){print(murders$abb[x])}
```

4. Create a function sum_n that for any given value, say  
n
 , computes the sum of the integers from 1 to n (inclusive). Use the function to determine the sum of integers from 1 to 5,000.
```{r}
sum_n <- n*(n+1)
n <- 5000
sum_n
```
5. Create a function altman_plot that takes two arguments, x and y, and plots the difference against the sum.
```{r}
altam_plot <- function(x,y)
plot(altam_plot)
#사실 문제의 뜻을 이해하지 못하겠다.
```
6. After running the code below, what is the value of x?
```{r}
x <- 3
my_func <- function(y){
  x <- 5
  y+5
}
x
```
7. Write a function compute_s_n that for any given  n computes the sum
Sn=1^2+2^2+…n^2. 
Report the value of the sum when  
n=10
.
```{r}
compute_s_n <- function(n){
  x <- 1:n 
  sum(x^2)
}
n <- 10
compute_s_n(10)
```
 8. Define an empty numerical vector s_n of size 25 using s_n <- vector("numeric", 25) and store in the results of  
S1,S2,…S25
using a for-loop.
```{r}
m <- 25
s_n <- vector(length =m)
for(n in 1:m){s_n[n] <- compute_s_n(n)}
s_n
```
9. Repeat exercise 8, but this time use `sapply`.
```{r}
x <- 1:25
sapply(x, compute_s_n)
```
10. Repeat exercise 8, but this time use map_dbl.
```{r}
?map_dbl
vector_1 <- c(1:25)
vector_1
map_dbl(x= vector_1, f= compute_s_n)
```
11. Plot  Sn versus  n. 
Use points defined by  n=1,…,25.
```{r}
n<-1:25
plot(n, s_n)
```
12. Confirm that the formula for this sum is  Sn=n(n+1)(2n+1)/
6
```{r}
x<-1:25
c <- function(x){
  x
  y <- x(x+1)(2*x+1)/6
}
slappy(x, c)
```
 

