---
3.2 The very basics
3.2.1 objects
---
If we want to solve quadractic dqutions of ax^2 + bx + c = 0, we can use solutions like this:
(-b- √(b^2-4ac))/2a and (-b+ √(b^2-4ac))/2a

a,b, and c is variables, so we can define values to variables.
For example, if we are asked to solve x^2 + x - 1 = 0, then we define:

```{r}
a <- 1
b <- 1
c <- -1
```

we can also assign values using '=', instead of '<-', but we recommend against using '=' to avoid confusion.

To see the value stored in a variable, we simply ask R to evaluate 'a' and it shows the stored value:
```{r}
a
```

A more explicit way to ask R to show us the value stored in 'a' is using 'print' like this:
```{r}
print(a)
```



---
3.2.2 The workspace
---

As we define objects in the console, we are actually changing the workspace. We can see all the variables saved in your workspace by typing:
```{r}
ls()
```

If we try to to recover the value of a variable that is not in our workspace, we receive an error.

Now since these values are saved in variables, to obtain a solution to our equation, we use the quadratic formula:
```{r}
(-b + sqrt(b^2 - 4*a*c) ) / ( 2*a )
(-b - sqrt(b^2 - 4*a*c) ) / ( 2*a )
```

unlike ls, most founctions require one or more 'arguments'.(argument:인수, 함수에 넘기는 어떤 값) Below is an example of how we assign an objects to the argument of the function 'log'.
```{r}
log(8)
log(a)
```

You can find out what the function expects and what it does by reviewing the very useful manuals included in R. You can get help by using the 'help' function like this:
```{r}
help(log)
```

for mos functions, we can also use this shorthand:
```{r}
?log
```

'help' page는 함수의 기본 설정 인수값이 무엇인지 보여준다. '='으로 표시되는 값이 default value. 예로 'log'는 'x' 와 'base'값이 필요한데, log의 base는 base = exp(1) 이라고 표시된데서 natural log가 default라는 것을 알 수 있다.

If you want a quick look at the arguments without opening the help system, you can type:
```{r}
args(log)
```

You can change the default values by simply assigning another object:
```{r}
log(8, base = 2)
```

Note that we have not been specifying the argument x as such:
```{r}
log(x=8, base =2)
```

Note that we have not been specifying the argument x as such: 따로 인수의 이름을 표기하지 않는 이상(x, base) help file 에 나온 순서대로 R은 인식한다.
So by not using the names, it assumes the arguments are x followed by base:
```{r}
log(8,2)
```

If using the arguments’ names, then we can include them in whatever order we want:
```{r}
log(base = 2, x = 8)
```

To specify arguments, we must use '=', and cannot use '<-'.

There are some exceptions to the rule that functions need the parentheses(괄호) to be evaluated. Among these, the most commonly used are the arithmetic(산수) and relational operators. For example:
```{r}
2^3
```

You can see the arithmetic operators by typing:
```{r}
help("+")
```
or
```{r}
?"+"
```
and the relational operators by typing:
```{r}
help(">")
```
or
```{r}
?">"
```


---
3.2.4. Other prebuilt objects
---
```{r}
install.packages("dslabs")
```
There are several datasets that are included for users to practice and test out functions. You can see all the available datasets by typing:
```{r}
data()
```

These datasets are objects that can be used by simply typing the name. For example, if you type co2, R will show you Mauna Loa atmospheric CO2 concentration data.
```{r}
co2
```
Other prebuilt objects are mathematical quantities, such as the constant  
π and  ∞ :
```{r}
pi
Inf+1
```


---
3.2.5 Variable names
---
variable names can be almost anything. 
Some basic rules in R are that variable names have to start with a letter, can’t contain spaces and should not be variables that are predefined in R.
변수는  문자로 시작해야되고, 띄우기 포함 그지고, 기존에 R에 정의되지 않은 것이어야함.
A nice convention to follow is to use meaningful words that describe what is stored, use only lower case, and use underscores as a substitute for spaces. For the quadratic equations, we could use something like this:
```{r}
solution_1 <- (-b + sqrt(b^2 - 4*a*c)) / (2*a)
solution_2 <- (-b - sqrt(b^2 - 4*a*c)) / (2*a)
```


---
3.2.6 Saving your workspace
---
Values remain in the workspace until you end your session or erase them with the function 'rm'.
we recommend you assign the workspace a specific name. You can do this by using the function 'save' or 'save.image'.
To load, use the function 'load'. When saving a workspace, we recommend the suffix 'rda' or 'RData'. In RStudio, you can also do this by navigating to the 'Session' tab and choosing 'Save Workspace' as. You can later load it using the 'Load Workspace' options in the same tab.


---
3.2.7 Motivationg scripts
---
To solve another equation such as  
3x^2 + 2x -1, 
we can copy and paste the code above and then redefine the variables and recompute the solution:
```{r}
a <- 3
b <- 2
C <- -1
(-b + sqrt(b^2 - 4*a*c)) / (2*a)
(-b - sqrt(b^2 - 4*a*c)) / (2*a)
```


---
3.2.8 Commenting your code
---
If a line of R code starts with the symbol #, it is not evaluated. We can use this to write reminders of why we wrote particular code. For example, in the script above we could add:
```{r}
## Code to compute solution to quadratic equation of the form ax^2 + bx + c
## define the variables
a <- 3 
b <- 2
c <- -1

## now compute the solution
(-b + sqrt(b^2 - 4*a*c)) / (2*a)
(-b - sqrt(b^2 - 4*a*c)) / (2*a)
```