---
title: "R Notebook"
output: html_notebook
---
# 3.7 Vectors
#### 3.7.1 Creating vectors

We can create vectors using the function `c`, which stands for concatenate. We use `c` to concatenate entries in the following way:
```{r}
codes <- c(380, 124, 818)
codes
```

We use the quotes to denote that the entries are characters rather than variable names.
character element를 포함할때는 ""표시
```{r}
country <- c("italy", "canada", "egypt")
```

In R you can also use single quotes:
```{r}
country <- c('italy', 'canada', 'egypt')
```

By now you should know that if you type:
```{r}
country <- c(italy, canada, egypt)
```
`italy`, `canada`, `egypt`를 변수로 인식해 해당 변수값이 없으므로 오류뜸


#### 3.7.2 Names

Sometimes it is useful to name the entries of a vector. For example, when defining a vector of country codes, we can use the names to connect the two:
```{r}
codes <- c(italy = 380, canada = 124, egypt = 818)
codes
```

The object `codes` continues to be a numeric vector:
```{r}
class(codes)
```
but with `names`:
```{r}
names(codes)
```

If the use of strings without quotes looks confusing, know that you can use the quotes as well:
```{r}
codes <- c("italy" = 380, "canada" = 124, "egypt" = 818)
codes
```

We can also assign `names` using the names functions:
```{r}
codes <- c(380, 124, 818)
country <- c("italy", "canada", "egytp")
names(codes) <- country
codes
```
`names`로 1vector에 2vector의 element를 제목? 처럼 매칭시킬수 있다.



#### 3.7.3 Sequences

Another useful function for creating vectors generates sequences:
```{r}
seq(1, 10)
```

`seq`(a,b,c)
a : 시작수
b : 끝수
c : 얼마씩 증가?(default:1)

hird argument lets us tell it how much to jump by:
```{r}
seq(1, 10, 2)
```
When we use these functions, R produces integers, not numerics, because they are typically used to index something:
```{r}
class(1:10)
```

However, if we create a sequence including non-integers, the class changes:
```{r}
class(seq(1, 10, 0.5))
```



#### 3.7.4 Subsetting
We use square brackets `[` to access specific elements of a vector. For the vector `codes` we defined above, we can access the second element using:
```{r}
codes[2]
```
You can get more than one entry by using a multi-entry vector as an index:
```{r}
codes[c(1,3)]
```
The sequences defined above are particularly useful if we want to access, say, the first two elements:
```{r}
codes[1:2]
```
If the elements have names, we can also access the entries using these names. Below are two examples.
```{r}
codes["canada"]
codes[c("egypt", "italy")]
```



# 3.8 Coercion
In general, coercion is an attempt by R to be flexible with data types.

We said that vectors must be all of the same type. So if we try to combine, say, numbers and characters, you might expect an error:
```{r}
x <- c(1, "canada", 3)
```

But we don’t get one, not even a warning! What happened? Look at `x` and its class:
```{r}
x
class(x)
```
R _coerced_ the data into characters.

R also offers functions to change from one type to another. For example, you can turn numbers into characters with:
```{r}
x <- 1:5
y <- as.character(x)
y
```

You can turn it back with `as.numeric`:
```{r}
as.numeric(y)
```


#### 3.8.1 Not availables(NA)
When a function tries to **coerce** one type to another and encounters an impossible case, it usually gives us a warning and turns the entry into a special value called an `NA` for “not available”. For example:
```{r}
x <- c("1", "b", "3")
as.numeric(x)
```
`b`의 해당 숫자가 무엇인지 모라 오류생김



#### 3.9 Exercises
1. Use the function `c` to create a vector with the average high temperatures in January for Beijing, Lagos, Paris, Rio de Janeiro, San Juan and Toronto, which are 35, 88, 42, 84, 81, and 30 degrees Fahrenheit. Call the object `temp`.
```{r}
temp <- c(35, 88, 42, 84, 81, 30)
temp
```

2. Now create a vector with the city names and call the object `city`.
```{r}
city <- c("Beijing", "Lagos", "Paris", "Rio de Janeiro", "San Juan", "Toronto")
city
```

3. Use the `names` function and the objects defined in the previous exercises to associate the temperature data with its corresponding city.
```{r}
names(temp) <- city
temp
```

4. Use the `[` and `:` operators to access the temperature of the first three cities on the list.
```{r}
temp[1:3]
```

5. Use the [ operator to access the temperature of Paris and San Juan.
```{r}
temp[c("Paris", "San Juan")]
#여러개 할때 c()잊지말기
```

6.Use the : operator to create a sequence of numbers  12,13,14,…,73. 
```{r}
12:73
```

7. Create a vector containing all the positive odd numbers smaller than 100.
```{r}
c <- seq(1,100,2)
c
```

8. Create a vector of numbers that starts at 6, does not pass 55, and adds numbers in increments of 4/7: 6, 6+4/7, 6+8/7, etc.. How many numbers does the list have? Hint: use `seq` and `length`.
```{r}
length(seq(6,55,4/7))
#86개
```

9. What is the class of the following object `a <- seq(1, 10, 0.5)?`
```{r}
a <- seq(1, 10, 0.5)
class(a)
#numeric
```

10. What is the class of the following object `a <- seq(1, 10)?`
```{r}
a <- seq(1, 10)
class(a)
#integer
```

11. The class of `class(a<-1)` is numeric, not integer. R defaults to numeric and to force an integer, you need to add the letter `L`. Confirm that the class of `1L` is integer.
```{r}
class(a <- 1)
class(a <- 1L)
```

12. Define the following vector:
`x <- c("1", "3", "5")`
and coerce it to get integers.
```{r}
x <- c("1", "3", "5")
y <- as.integer(x)
class(y)
```



# 3.10 Sorting
#### 3.10.1 `sort`

Say we want to rank the states from least to most gun murders. The function `sort` sorts a vector in increasing order. We can therefore see the largest number of gun murders by typing:
```{r}
install.packages("dslabs")
library(dslabs)
data(murders)
sort(murders$total)
```




#### 3.10.2 `order`
The function `order` is closer to what we want. It takes a vector as input and returns the vector of indexes that sorts the input vector. This may sound confusing so let’s look at a simple example. We can create a vector and sort it:
```{r}
x <- c(31, 4, 15, 92, 65)
sort(x)
```
Rather than sort the input vector, the function order returns the index that sorts input vector:
```{r}
index <- order(x)
x[index]
```

This is the same output as that returned by `sort(x)`. If we look at this index, we see why it works:
```{r}
x
order(x)
```


How does this help us order the states by murders? First, remember that the entries of vectors you access with `$` follow the same order as the rows in the table. For example, these two vectors containing state names and abbreviations respectively are matched by their order:
```{r}
murders$state[1:10]

murders$abb[1:10]
```

This means we can order the state names by their total murders. We first obtain the index that orders the vectors according to murder totals and then index the state names vector:
```{r}
ind <- order(murders$total)
murders$abb[ind]
```



#### 3.10.3 `max` and `which.max`
If we are only interested in the entry with the largest value, we can use `max` for the value:
```{r}
max(murders$total)
```

and `which.max` for the index of the largest value:
```{r}
i_max <- which.max(murders$total)
murders$state[i_max]
```
For the minimum, we can use `min` and `which.min` in the same way.

#### 3.10.4 rank
`rank` is useful. For any given vector it returns a vector with the rank of the first entry, second entry, etc., of the input vector. Here is a simple example:
```{r}
x <- c(31, 4, 15, 92, 65)
rank(x)
```


#### 3.10.5 Beware of recycling
If the vectors don’t match in length, it is natural to assume that we should get an error. But we don’t. Notice what happens:
```{r}
x <- c(1,2,3)
y <- c(10, 20, 30, 40, 50, 60, 70)
x+y
```



# 3.11 Exercise
1. Use the `$` operator to access the population size data and store it as the object `pop`. Then use the `sort` function to redefine `pop` so that it is sorted. Finally, use the `[` operator to report the smallest population size.
```{r}
pop <- (murders$population)
sort_pop <- sort(pop)
sort_pop[1]
```

2. Now instead of the smallest population size, find the index of the entry with the smallest population size. Hint: use `order` instead of `sort`.
```{r}
pop
order(pop)[1]
#51
```

3. We can actually perform the same operation as in the previous exercise using the function `which.min`. Write one line of code that does this.
```{r}
which.min(pop)
#51
```

4. Now we know how small the smallest state is and we know which row represents it. Which state is it? Define a variable `states` to be the state names from the `murders` data frame. Report the name of the state with the smallest population.
```{r}
states <- murders$state
states[which.min(pop)]
```

5. You can create a data frame using the data.frame function. Here is a quick example:
Use the `rank` function to determine the population rank of each state from smallest population size to biggest. Save these ranks in an object called `ranks`, then create a data frame with the state name and its rank. Call the data frame `my_df`.
```{r}
ranks <- rank(pop)
my_df <- data.frame(states, ranks)
my_df
```

6. Repeat the previous exercise, but this time order `my_df` so that the states are ordered from least populous to most populous. Hint: create an object `ind` that stores the indexes needed to order the population values. Then use the bracket operator `[` to re-order each column in the data frame.
```{r}
ind <- order(pop)
my_df$states[ind]
my_df$ranks[ind]
```
7. The `na_example` vector represents a series of counts. You can quickly examine the object using:
However, when we compute the average with the function `mean`, we obtain an NA:
The `is.na` function returns a logical vector that tells us which entries are `NA`. Assign this logical vector to an object called `ind` and determine how many NAs does `na_example` have.
```{r}
ind <- is.na(na_example)
sum(ind)
```

8. Now compute the average again, but only for the entries that are not NA. Hint: remember the ! operator.
```{r}
mean(na_example[!ind])
```



# 3.12 Vector arithmetics
California had the most murders, but does this mean it is the most dangerous state? What if it just has many more people than any other state? We can quickly confirm that California indeed has the largest population:
```{r}
library(dslabs)
data("murders")
murders$state[which.max(murders$population)]
```

#### 3.12.1 Rescaling a vector
In R, arithmetic operations on vectors occur element-wise. For a quick example, suppose we have height in inches:
```{r}
inches <- c(69, 62, 66, 70, 70, 73, 67, 73, 67, 70)
```
and want to convert to centimeters. Notice what happens when we multiply inches by 2.54:
```{r}
inches * 2.54
```
Similarly, if for each entry we want to compute how many inches taller or shorter than 69 inches, the average height for males, we can subtract it from every entry like this:
```{r}
inches - 69
```

#### 3.12.2 Two vectors
If we have two vectors of the same length, and we sum them in R, they will be added entry by entry as follows:
 a     e     a + e
 b     f     b + f
 c  +  g  =  c + g
 d     h     d + h
The same holds for other mathematical operations, such as `-`, `*`and `/`.
 
This implies that to compute the murder rates we can simply type:
```{r}
murder_rate <- murders$total / murders$population * 100000
```
Once we do this, we notice that California is no longer near the top of the list. In fact, we can use what we have learned to order the states by murder rate:
```{r}
murders$state[order(murder_rate)]
```


# 3.13 Exercises
1. Previously we created this data frame:
```{r}
temp <- c(35, 88, 42, 84, 81, 30)
city <- c("Beijing", "Lagos", "Paris", "Rio de Janeiro", "San Juan", "Toronto")
city_temps <- data.frame(name = city, temperature = temp)
```
Remake the data frame using the code above, but add a line that converts the temperature from Fahrenheit to Celsius.
```{r}
A <- 5/9*(temp - 31)
B <- data.frame(A, city)
B
```

2. What is the following sum?
Hint: thanks to Euler, we know it should be close to  π^2/6.
```{r}
data_1 <- seq(1,100)
data_2 <- 1 + data_1^2
data_2
```

3. Compute the per 100,000 murder rate for each state and store it in the object `murder_rate`. Then compute the average murder rate for the US using the function `mean`. What is the average?
```{r}
murder_rate <- (murders$total/murders$population*1000000)
mean(murder_rate)
```



# 3.14 Indexing
#### 3.14.1 Subsetting with logicals
We have now calculated the murder rate using:
```{r}
murder_rate <- murders$total / murders$population * 100000
```
Imagine you are moving from Italy where, according to an ABC news report, the murder rate is only 0.71 per 100,000. You would prefer to move to a state with a similar murder rate. Another powerful feature of R is that we can we can use logicals to index vectors. If we compare a vector to a single number, it actually performs the test for each entry. The following is an example related to the question above:
```{r}
ind <- murder_rate < 0.71
ind
```
If we instead want to know if a value is less or equal, we can use:
```{r}
ind <- murder_rate <= 0.71
ind
```

Note that we get back a logical vector with `TRUE` for each entry smaller than or equal to 0.71. To see which states these are, we can leverage the fact that vectors can be indexed with logicals.
```{r}
murders$state[ind]
```
In order to count how many are TRUE, the function `sum` returns the sum of the entries of a vector and logical vectors get coerced to numeric with `TRUE` coded as 1 and `FALSE` as 0. Thus we can count the states using:
```{r}
sum(ind)
```

#### 3.14.2 Logical operators
Here we can use the logical operator **and**, which in R is represented with `&`. This operation results in `TRUE` only when both logicals are `TRUE`. To see this, consider this example:
```{r}
TRUE & TRUE
TRUE & FALSE
FALSE & FALSE
```
For our example, we can form two logicals:
```{r}
west <- murders$region == "West"
safe <- murder_rate <= 1
```
and we can use the & to get a vector of logicals that tells us which states satisfy both conditions:
```{r}
ind <- safe & west
murders$state[ind]
```

#### 3.14.3 `which`
The function which tells us which entries of a logical vector are TRUE. So we can type:
```{r}
ind <- which(murders$state == "California")
murder_rate[ind]
```

#### 3.14.4 `match`
`match`
This function tells us which indexes of a second vector match each of the entries of a first vector:
```{r}
ind <- match(c("New York", "Florida", "Texas"), murders$state)
ind

```

Now we can look at the murder rates:
```{r}
murder_rate[ind]
```


#### 3.14.5 `%in%`
If rather than an index we want a logical that tells us whether or not each element of a first vector is in a second, we can use the function `%in%`.
Let’s imagine you are not sure if Boston, Dakota and Washington are states. You can find out like this:
```{r}
c("Boston", "Dakota", "Washington") %in% murders$state
```

**Advanced**
There is a connection between match and %in% through which. To see this, notice that the following two lines produce the same index (although in different order):
```{r}
match(c("New York", "Florida", "Texas"), murders$state)
which(murders$state%in%c("New York", "Florida", "Texas"))
```


# 3.15 Exercises
1. Compute the per 100,000 murder rate for each state and store it in an object called `murder_rat`e. Then use logical operators to create a logical vector named low that tells us which entries of `murder_rate` are lower than 1.
```{r}
murder_rate <- murders$total/murders$population*100000
low <- murder_rate < 1
low
```

2. Now use the results from the previous exercise and the function `which` to determine the indices of `murder_rate` associated with values lower than 1.
```{r}
which(low)
#which : logical 벡터의 참에 해당하는 index 보여줌
```

3. Use the results from the previous exercise to report the names of the states with murder rates lower than 1.
```{r}
murders$state[which(low)]
```

4. Now extend the code from exercise 2 and 3 to report the states in the Northeast with murder rates lower than 1. Hint: use the previously defined logical vector `low` and the logical operator `&`.
```{r}
Northeast <- murders$region == "Northeast"

ind <- Northeast&low
murders$state[ind]
```

5.In a previous exercise we computed the murder rate for each state and the average of these numbers. How many states are below the average?
```{r}
ave <- mean(murder_rate)
ind <- murder_rate < ave
length(murders$state[ind])
#27
```

6. Use the match function to identify the states with abbreviations AK, MI, and IA. Hint: start by defining an index of the entries of `murders$abb` that match the three abbreviations, then use the `[` operator to extract the states.
```{r}
ind <- match(c("AK", "MI", "IA"), murders$abb)
murders$state[ind]
```

7. Use the `%in%` operator to create a logical vector that answers the question: which of the following are actual abbreviations: MA, ME, MI, MO, MU ?
```{r}
log <- c("MA", "ME", "MI", "MO", "MU")%in%murders$abb
log
#MU 빼고 모든 지역 포함되있음.
```

8. Extend the code you used in exercise 7 to report the one entry that is not an actual abbreviation. Hint: use the `!` operator, which turns `FALSE` into TRUE and vice versa, then `which` to obtain an index.
```{r}
group <- c("MA", "ME", "MI", "MO", "MU")
group[which(!log == "TRUE")]
```




# 3.16 Basic plots
#### 3.16.1 `plot`

The `plot` function can be used to make scatterplots. Here is a plot of total murders versus population.
```{r}
x <- murders$population / 10^6
y <- murders$total

plot(x,y)
```

For a quick plot that avoids accessing variables twice, we can use the `with` function:
```{r}
with(murders, plot(population, total))
```
The function `with` lets us use the murders column names in the `plot` function. It also works with any data frames and any function.

#### 3.16.2 `hist`
```{r}
x <- with(murders, total / population * 100000)
hist(x)
```
We can see that there is a wide range of values with most of them between 2 and 3 and one very extreme case with a murder rate of more than 15:
```{r}
murders$state[which.max(x)]
```

#### 3.16.3 `boxplot`
 They provide a more terse summary than histograms, but they are easier to stack with other boxplots. For example, here we can use them to compare the different regions:
```{r}
murders$rate <- with(murders, total / population * 100000)
boxplot(rate~region, data = murders)
```

#### 3.16.4 image
The image function displays the values in a matrix using color. Here is a quick example:
```{r}
x <- matrix(1:120, 12, 10)
image(x)
```



# 3.17 Exercises
1. We made a plot of total murders versus population and noted a strong relationship. Not surprisingly, states with larger populations had more murders.
```{r}
library(dslabs)
data(murders)
population_in_millions <- murders$population/10^6
total_gun_murders <- murders$total
plot(population_in_millions, total_gun_murders)
```
Keep in mind that many states have populations below 5 million and are bunched up. We may gain further insights from making this plot in the log scale. Transform the variables using the `log10` transformation and then plot them.
```{r}
pop_2 <- log(x = murders$population/10^6, base = 10)
total_2 <- log(x = murders$total, base = 10)
plot(pop_2, total_2)
```

2. Create a histogram of the state populations.
```{r}
hist(murders$population)
```

3. Generate boxplots of the state populations by region.
```{r}
pop <- murders$population
region <- murders$region
boxplot(pop~region, data = murders)
```
