---
title: "R Notebook"
output: html_notebook
---
# Chapter 5 The tidyverse
`tidy`:data의 한 종류
`tidyverse` : package, tidy 이용에 유리
 
We can load all the tidyverse packages at once by installing and loading the `tidyverse` package:
```{r}
install.packages("tidyverse")
install.packages("dslabs")
library(tidyverse)
```

in `tidyverse`: 'dplyr', 'purrr', and 'ggplot2' packages.



#### 5.1 Tidy data
We say that a data table is in `tidy` format if each row represents one observation and columns represent the different variables available for each of these observations. 
`tidy` : row(행,가로) : one obsevation
         column(열) : different variables
         
The `murders` dataset is an example of a tidy data frame.
```{r}
library(dslabs)
murders
```
Each row represent a state with each of the five columns providing a different variable related to these states: name, abbreviation, region, population, and total murders.

To see how the same information can be provided in different formats, consider the following example:
```{r}
#>        country year fertility
#> 1      Germany 1960      2.41
#> 2  South Korea 1960      6.16
#> 3      Germany 1961      2.44
#> 4  South Korea 1961      5.99
#> 5      Germany 1962      2.47
#> 6  South Korea 1962      5.79
#> 7      Germany 1963      2.49
#> 8  South Korea 1963      5.57
#> 9      Germany 1964      2.49
#> 10 South Korea 1964      5.36
#> 11     Germany 1965      2.48
#> 12 South Korea 1965      5.16
```
This is a tidy dataset because each row presents one observation with the three variables being county, year and fertility rate.

Originally, the data was in the following format:
```{r}
#>       country 1960 1961 1962 1963 1964 1965
#> 1     Germany 2.41 2.44 2.47 2.49 2.49 2.48
#> 2 South Korea 6.16 5.99 5.79 5.57 5.36 5.16
```
This is not tidy format.
1. each row include several observations.
2. the same variable, year is stored in the header.

For the tidyverse packages to be optimally used, data need to be reshaped into `tidy` format.
`tidyverse`package 사용을 위해선 `tidy`format이어야함.




# 5.2 Exercises
1. Examine the built-in dataset `co2`. Which of the following is true:
```{r}
co2
#row에 여러개의 observation이 있다 > tidy data 가 아니다.
class(co2)
#C
```

2. Examine the built-in dataset `ChickWeight`. Which of the following is true:
```{r}
ChickWeight
class(ChickWeight)
#D
```
3. Examine the built-in dataset BOD. Which of the following is true:
```{r}
BOD
#C
```
4. Which of the following built-in datasets is tidy (you can pick more than one):
```{r}
BJsales
EuStockMarkets
DNase
Formaldehyde
Orange
UCBAdmissions
#B,C,D,E
```



# 5.3 Manipulating data frames
The `dplyr` package from the `tidyverse`
:to change the data table by adding a new column, we use `mutate`.
To filter the data table to a subset of rows, we use `filter`. 
Finally, to subset the data by selecting specific columns, we use `select`.

#### 5.3.1 Adding a column with `mutate`
**The function `mutate` takes the data frame as a first argument and the name and values of the variable as a second argument using the convention `name = values`.**

So, to add murder rates, we use:
```{r}
library(dslabs)
data("murders")
murders <- mutate(murders, rate = total / population*100000)
```
*dplyr 에서는 first argument의 data frame variable은 자동으로 인식함
*원 `murders` data frame은 그대로이므로 `date(murders)`를 다시 실행하면 original data frame 실행

We can see that the new column is added:
```{r}
head(murders)
```


#### 5.3.2 Subsetting with `filter`
Now suppose that we want to filter the data table to only show the entries for which the murder rate is lower than 0.71. **To do this we use the filter function, which takes the data table as the first argument and then the conditional statement as the second.**
* `!=` : remove row
 ex) filter(murders, state! = "Florida")
     >Florida 제외 state들만 표시
```{r}
filter(murders, rate <= 0.71)
```


#### 5.3.3 Selecting columns with `select`
If we want to view just a few, we can use the **dplyr** `select` function.
```{r}
new_table <- select(murders, state, region, rate)
filter(new_table, rate <= 0.71)
```
In the call to `select`, the first argument `murders` is an object, but `state`, `region`, and `rate` are variable names.



# 5.4 Exercises
1. Load the dplyr package and the murders dataset.
```{r}
library(dplyr)
library(dslabs)
data(murders)
```
You can add columns using the **dplyr** function `mutate`. This function is aware of the column names and inside the function you can call them unquoted:
```{r}
murders <- mutate(murders, population_in_millions = population / 10^6)
```
We can write `population` rather than `murders$population`. The function `mutate` knows we are grabbing columns from `murders`.

Use the function `mutate` to add a murders column named `rate` with the per 100,000 murder rate as in the example code above. Make sure you redefine `murders` as done in the example code above ( murders <- [your code]) so we can keep using this variable.
```{r}
murders <- mutate(murders, rate = total / population * 100000)
murders
```

2. If `rank(x)` gives you the ranks of x from lowest to highest, `rank(-x)` gives you the ranks from highest to lowest. Use the function `mutate` to add a column rank containing the `rank`, from highest to lowest murder rate. Make sure you redefine `murders` so we can keep using this variable.
```{r}
murders <- mutate(murders, rank=rank(-rate))
murders
```

3. With **dplyr**, we can use `select` to show only certain columns. For example, with this code we would only show the states and population sizes:
```{r}
select(murders, state, population) %>% head()
```
Use `select` to show the state names and abbreviations in `murders`. Do not redefine `murders`, just show the results.
```{r}
select(murders, state, abb)
```

4. The **dplyr** function `filter` is used to choose specific rows of the data frame to keep. Unlike `select` which is for columns, `filter` is for rows. For example, you can show just the New York row like this:
```{r}
filter(murders, state == "New York")
```
You can use other logical vectors to filter rows.

Use `filter` to show the top 5 states with the highest murder rates. After we add murder rate and rank, do not change the murders dataset, just show the result. Remember that you can filter based on the `rank` column.
```{r}
filter(murders, rank <= 5)
```

5. We can remove rows using the `!=` operator. For example, to remove Florida, we would do this:
```{r}
no_florida <- filter(murders, state != "Florida")
```
Create a new data frame called `no_south` that removes states from the South region. How many states are in this category? You can use the function `nrow` for this.
**nrow : row의 수를 측정하는 function**
```{r}
no_south <- filter(murders, region != "South")
nrow(no_south)
#34
```

6. We can also use `%in%` to filter with **dplyr**. You can therefore see the data from New York and Texas like this:
```{r}
filter(murders, state %in% c("New York", "Texas"))
```
Create a new data frame called `murders_nw` with only the states from the Northeast and the West. How many states are in this category?
```{r}
murders_nw <- filter(murders, region %in% c("Northeast", "West"))
nrow(murders_nw)
#22
```

7. Suppose you want to live in the Northeast or West and want the murder rate to be less than 1. We want to see the data for the states satisfying these options. Note that you can use logical operators with `filter`. Here is an example in which we filter to keep only small states in the Northeast region.
```{r}
filter(murders, population < 5000000 & region == "Northeast")
```
Make sure `murders` has been defined with `rate` and `rank` and still has all states. Create a table called `my_states` that contains rows for states satisfying both the conditions: it is in the Northeast or West and the murder rate is less than 1. Use `select` to show only the state name, the rate and the rank.
```{r}
my_states <- filter(murders, region %in% c("Northeast", "West") & rate < 1)
select(my_states, state, rate, rank)
```

# 5.5 The pipe: `%>%`
With **dplyr** we can perform a series of operations, for example `select` and then `filter`, by sending the results of one function to another using what is called the pipe operator: `%>%`.
**`%>%` : dplyr 안에서 operation 여러개를 동시진행(왼쪽의 결과를 오른쪽 function의 first argument로 처리)**
**intermediate object 발생x**

**original data → select → filter** 
 

For such an operation, we can use the pipe %>%. The code looks like this:
```{r}
murders %>% select(state, region, rate) %>% filter(rate <= 0.71)
```

In general, the pipe sends the result of the left side of the pipe to be the first argument of the function on the right side of the pipe. Here is a very simple example:
```{r}
16 %>% sqrt()
```

We can continue to pipe values along:
```{r}
16 %>% sqrt() %>% log2()
```
The above statement is equivalent to `log2(sqrt(16))`.

Remember that the pipe sends values to the first argument, so we can define other arguments as if the first argument is already defined:
```{r}
16 %>% sqrt() %>% log(base = 2)
```
Therefore, when using the pipe with data frames and **dplyr**, we no longer need to specify the required first argument since the **dplyr** functions we have described all take the data as the first argument. In the code we wrote:
```{r}
murders %>% select(state, region, rate) %>% filter(rate <= 0.71)
```
`murders` is the first argument of the `select` function, and the new data frame (formerly `new_table`) is the first argument of the `filter` function.

Note that the pipe works well with functions where the first argument is the input data. Functions in **tidyverse** packages like **dplyr** have this format and can be used easily with the pipe.



# 5.6 Exercises

1. The pipe `%>%` can be used to perform operations sequentially without having to define intermediate objects. Start by redefining murder to include rate and rank.
```{r}
murders <- mutate(murders, rate =  total / population * 100000, rank = rank(-rate))
```
In the solution to the previous exercise, we did the following:
```{r}
my_states <- filter(murders, region %in% c("Northeast", "West") & rate < 1)

select(my_states, state, rate, rank)
```
The pipe `%>%` permits us to perform both operations sequentially without having to define an intermediate variable `my_states`. We therefore could have mutated and selected in the same line like this:
```{r}
mutate(murders, rate =  total / population * 100000, rank = rank(-rate)) %>%
  select(state, rate, rank)
```
Notice that `select` no longer has a data frame as the first argument. The first argument is assumed to be the result of the operation conducted right before the %>%.

Repeat the previous exercise, but now instead of creating a new object, show the result and only include the state, rate, and rank columns. Use a pipe `%>%` to do this in just one line.
```{r}
filter(murders, region %in% c("Northeast", "West") & rate < 1) %>% select(state, rate, rank)
```

2. Reset `murders` to the original table by using `data(murders)`. Use a pipe to create a new data frame called `my_states` that considers only states in the Northeast or West which have a murder rate lower than 1, and contains only the state, rate and rank columns. The pipe should also have four components separated by three `%>%`. The code should look something like this:
```{r}
data(murders)
my_states <- murders %>% mutate(rate = total / population * 100000, rank = rank(-rate)) %>% filter(region %in% c("Northeast", "West") & rate < 1 ) %>% select(state, rate, rank)
my_states
#**Northeast or West이므로 `==`이 아니라 `%in%을 쓴다**
```



# 5.7 Summarizing data
we cover two new **dplyr** verbs that make these computations easier: 
`summarize` and `group_by`. We learn to access resulting values using the `pull` function.


# 5.7.1 `summarize`
**`Summarize`:summary statistic 계산**
**새로운 table 형성, return data frame.**
**Summarize(original data table, 새 column1 이름=function1, 새 column2 이름=function2...)**
**2개 이상의 value return x**
**`quantile`:quantile(0,0.5,1)->min,medium,max 송출**

The `summarize` function in **dplyr** provides a way to compute summary statistics with intuitive and readable code. We start with a simple example based on heights. The heights dataset includes heights and sex reported by students in an in-class survey.
```{r}
library(dplyr)
library(dslabs)
data(heights)
```

The following code computes the average and standard deviation for females:
```{r}
s <- heights %>% 
  filter(sex == "Female") %>%
  summarize(average = mean(height), standard_deviation = sd(height))
s
```
We get to choose the names of the columns of the resulting table.

Because the resulting table stored in s is a data frame, we can access the components with the accessor $:
```{r}
s$average
s$standard_deviation
```
As with most other **dplyr** functions, `summarize` is aware of the variable names and we can use them directly.

We can compute any other summary that operates on vectors and returns a **single value**.
For example, we can add the median, min and max heights like this:
```{r}
heights %>% 
  filter(sex == "Female") %>%
  summarize(median = median(height), minimum = min(height), maximum = max(height))
```

We can obtain these three values with just one line using the `quantile` function: for example, `quantile(x, c(0,0.5,1))` returns the min (0th percentile), median (50th percentile), and max (100th percentile) of the vector x. However, if we attempt to use a function like this that returns two or more values inside `summarize`:
```{r}
heights %>% 
  filter(sex == "Female") %>%
  summarize(range = quantile(height, c(0, 0.5, 1)))
```
we will receive an error: `Error: expecting result of length one, got : 2`. With the function `summarize`, we can only call functions that return a single value.

For another example of how we can use the `summarize` function, let’s compute the average murder rate for the United States. Remember our data table includes total murders and population size for each state and we have already used **dplyr** to add a murder rate column:
```{r}
data(murders)
murders <- murders %>% mutate(rate = total/population*100000)
```
Remember that the US murder rate is not the average of the state murder rates:
```{r}
summarize(murders, mean(rate))
```
This is because in the computation above the small states are given the same weight as the large ones. The US murder rate is the total number of murders in the US divided by the total US population. So the correct computation is:
```{r}
us_murder_rate <- murders %>%
  summarize(rate = sum(total) / sum(population) * 100000)
us_murder_rate
```
This computation counts larger states proportionally to their size which results in a larger value.
**U.S의 평균을 구하려면 state rate의 평균이 아닌 sum(totla)/sum(pop)을 해야된다. state rate는 모든 값을 state 크기에 관계없이 동일하게 취급**



#### 5.7.2 `pull`
**pull:data.frame의 column값을 numeric으로 추출하고 싶을 때 사용**
**pull(dataframe, 추출column):`$`와 비슷**

The `us_murder_rate` object defined above represents just one number. Yet we are storing it in a data frame:
```{r}
class(us_murder_rate)
```

**since, as most dplyr functions, summarize always returns a data frame.**
Here we show a useful trick for accessing values stored in data when using pipes: when a data object is piped that object and its columns can be accessed using the `pull` function. To understand what we mean take a look at this line of code:
```{r}
us_murder_rate %>% pull(rate)
```

This returns the value in the `rate` column of `us_murder_rate` making it equivalent to `us_murder_rate$rate`.

To get a number from the original data table with one line of code we can type:
```{r}
us_murder_rate <- murders %>% 
  summarize(rate = sum(total) / sum(population) * 100000) %>%
  pull(rate)

us_murder_rate
```
which is now a numeric:
```{r}
class(us_murder_rate)
```



#### 5.7.3 Group then summarize with `group_by`

**`group_by`: 하나의 기준으로 data를 나눔 -> 이후 function은 각 group에 seperately 적용**

A common operation in data exploration is to first split data into groups and then compute summaries for each group.
The `group_by` function helps us do this.
```{r}
heights %>% group_by(sex)
```
The result does not look very different from `heights`, except we see `Groups: sex [2]` when we print the object.
Although not immediately obvious from its appearance, this is now a special data frame called a _grouped data frame_ and **dplyr** functions, in particular `summarize`, will behave differently when acting on this object. Conceptually, you can think of this table as many tables, with the same columns but not necessarily the same number of rows, stacked together in one object. When we summarize the data after grouping, this is what happens:
```{r}
heights %>% 
  group_by(sex) %>%
  summarize(average = mean(height), standard_deviation = sd(height))
```
The `summarize` function applies the summarization to each group separately.

For another example, let’s compute the median murder rate in the four regions of the country:
```{r}
murders %>% 
  group_by(region) %>%
  summarize(median_rate = median(rate))
```



# 5.8 Sorting data frames

When examining a dataset, it is often convenient to sort the table by the different columns. We know about the `order` and `sort` function, but for ordering entire tables, the **dplyr** function `arrange` is useful. For example, here we order the states by population size:
```{r}
murders %>%
  arrange(population) %>%
  head()
```

With `arrange` we get to decide which column to sort by. To see the states by population, from smallest to largest, we arrange by `rate` instead:
**`arrange`:한 dataset의 하나의 column을 기준으로 전체 data를 정렬**
**`arrange(정렬할 dataset, 기준column1, 기준 column2, 기준column3...)**
**default:작->큰, _dplyr_ 에선 `desc`씀 : arrnage(desc(rate))**

Note that the default behavior is to order in ascending order. In **dplyr**, the function `desc` transforms a vector so that it is in descending order. To sort the table in descending order, we can type:
```{r}
murders %>% 
  arrange(desc(rate)) %>% 
  head()
```



#### 5.8.1 Nexted Sorting
If we are ordering by a column with ties, we can use a second column to break the tie. Similarly, a third column can be used to break ties between first and second and so on. Here we order by `region`, then within region we order by murder rate:
```{r}
murders %>% 
  arrange(region, rate) %>% 
  head()
```


#### 5.8.2 The top n
**`top_n`:`head`보다 더 많은 정보의 data를 보고 싶을 때**
**`top_n(dataframe, row수, filter될 column(only filter! sort 위해선 `arrange`사용))**

In the code above, we have used the function `head` to avoid having the page fill up with the entire dataset. If we want to see a larger proportion, we can use the `top_n` function. This function takes a data frame as it’s first argument, the number of rows to show in the second, and the variable to filter by in the third. Here is an example of how to see the top 10 rows:
```{r}
murders %>% top_n(10, rate)
```



# 5.9 Exercises
**ignore "NA" : `na.rm` : mean(na_exmaple, na.rm = TRUE) > 값나옴**

```{r}
install.packages("NHANES")
library(NHANES)
data(NHANES)
```

To ignore the NAs we can use the na.rm argument:
```{r}
mean(na_example, na.rm = TRUE)
sd(na_example, na.rm = TRUE)
```


1. We will provide some basic facts about blood pressure. First let’s select a group to set the standard. We will use 20-29 year old females. `AgeDecade` is a categorical variable with these ages. Note that the category is coded like " 20-29“, with a space in front! What is the average and standard deviation of systolic blood pressure as saved in the `BPSysAve` variable? Save it to a variable called `ref`.

Hint: Use `filter` and `summarize` and use the `na.rm = TRUE` argument when computing the average and standard deviation. You can also filter the NA values using `filter`.
```{r}
ref <- NHANES %>% filter(Gender=="female" & AgeDecade==" 20-29") %>% summarize(average = mean(BPSysAve, na.rm = TRUE), standard_deviation = sd(BPSysAve, na.rm=TRUE))
ref
#`na.rm=TRUE`는 각 function의 ()안에 들어가야함.
```

2. Using a pipe, assign the average to a numeric variable `ref_avg`. Hint: Use the code similar to above and then `pull`.
```{r}
ref_avg <- ref %>% pull(average)
ref_avg
class(ref_avg)
```

3. Now report the min and max values for the same group.
```{r}
NHANES %>% filter(Gender == "female" & AgeDecade == " 20-29") %>% summarize(minimum = min(BPSysAve, na.rm = TRUE), maximum = max(BPSysAve, na.rm = TRUE))
```

4. Compute the average and standard deviation for females, but for each age group separately rather than a selected decade as in question 1. Note that the age groups are defined by `AgeDecade`. Hint: rather than filtering by age and gender, filter by `Gender` and then use `group_by`.
```{r}
NHANES %>% filter(Gender == "female") %>% group_by(AgeDecade) %>% summarize(average = mean(BPSysAve, na.rm = TRUE), standard_deviation = sd(BPSysAve, na.rm = TRUE))
```

5. Repeat exercise 4 for males.
```{r}
NHANES %>% filter(Gender == "male") %>% group_by(AgeDecade) %>% summarize(average = mean(BPSysAve, na.rm = TRUE), standard_deviation = sd(BPSysAve, na.rm = TRUE))
```

6. We can actually combine both summaries for exercises 4 and 5 into one line of code. This is because `group_by` permits us to group by more than one variable. Obtain one big summary table using `group_by(AgeDecade, Gender)`.
```{r}
NHANES %>% group_by(AgeDecade, Gender) %>% summarize(average = mean(BPSysAve, na.rm = TRUE), standard_deviation = sd(BPSysAve, na.rm = TRUE))
```

7. For males between the ages of 40-49, compare systolic blood pressure across race as reported in the `Race1` variable. Order the resulting table from lowest to highest average systolic blood pressure.
```{r}
NHANES %>% filter(Gender == "male", AgeDecade == " 40-49") %>% arrange(Race1)
```



# 5.10 Tibbles
**'tbl'**
**: tibble, data frame의 한 종류**
**tidyverse에 적합한 형태**
**'group_by', 'summarize' function의 출력형태**
**c.f) `group_by`: grouped_df 종류의 tibble 출력**
_select, filter, mutate, arrange는 입력값과 같은 형태의 data종류 출력_

Tidy data must be stored in data frames. We introduced the data frame in Section 3.5 and have been using the `murders` data frame throughout the book:
```{r}
data(murders)
class(murders)
```

In Section 5.7.3 we introduced the `group_by` function, which permits stratifying data before computing summary statistics. But where is the group information stored in the data frame?
```{r}
murders %>% group_by(region) %>% head()
```

Notice that there are no columns with this information. But, if you look closely at the output above, you see the line `A tibble: 6 x 5`. We can learn the class of the returned object using:
```{r}
murders %>% group_by(region) %>% class()
```

Tibbles are very similar to data frames. In fact, you can think of them as a modern version of data frames. Nonetheless there are three important differences which we describe in the next.
_세가지 data.frames와 tibble의 차이점에 관하여_


#### 5.10.1 Tibbles display better
**`as_tibble`:tibble 형태로 바꿈**
**ex)as_tibble(murders)**

The print method for tibbles is more readable than that of a data frame. To see this, compare the outputs of typing `murders` and the output of murders if we convert it to a tibble. We can do this using `as_tibble(murders)`. If using RStudio, output for a tibble adjusts to your window size. To see this, change the width of your R console and notice how more/less columns are shown.
```{r}
murders
murders_new <- as_tibble(murders)
murders_new
```



#### 5.10.2 Subsets of tibbles are tibbles
**data frame을 subset하면 dataframe이 안나오지만 tibble을 subset(특정값 추출?)하면 dataframe이 출력되 function의 입력값으로 사용하기 유리하다.**

**tibble 입력시 dataframe이 안나오게 하려면 accessor `$` 사용**

**tibble의 경우 NULL에 대해 설명해주어 debug에 유리**


If you subset the columns of a data frame, you may get back an object that is not a data frame, such as a vector or scalar. For example:
```{r}
class(murders[,4])
```
is not a data frame. With tibbles this does not happen:
```{r}
class(as_tibble(murders)[,4])
```
This is useful in the tidyverse since functions require data frames as input.

With tibbles, if you want to access the vector that defines a column, and not get back a data frame, you need to use the accessor `$`:
```{r}
class(as_tibble(murders)$population)
```

A related feature is that tibbles will give you a warning if you try to access a column that does not exist. If we accidentally write `Population` instead of `population` this:
```{r}
murders$Population
```

returns a NULL with no warning, which can make it harder to debug. In contrast, if we try this with a tibble we get an informative warning:
```{r}
as_tibble(murders)$Population
```



#### 5.10.3 Tibbles can have complex entries
**tibble's column can be more diverse, like function or lists.**

While data frame columns need to be vectors of numbers, strings or logical values, tibbles can have more complex objects, such as lists or functions. Also, we can create tibbles with functions:
```{r}
tibble(id = c(1, 2, 3), func = c(mean, median, sd))
```


#### 5.10.4 Tibbles can be grouped

The function `group_by` returns a special kind of tibble: a grouped tibble. This class stores information that lets you know which rows are in which groups. The tidyverse functions, in particular the `summarize` function, are aware of the group information.


#### 5.10.5 Create a tibble using `data_frame` istead of `data.frame`

**`data_frame` : data frame 생성**
**`data.frame`** 
**: data frame 생성**
**chractor 를 factor로 coerce. 막으려면 cumbersome argument:`stringAsFactors=FALSE`추가**

It is sometimes useful for us to create our own data frames. To create a data frame in the tibble format, you can do this by using the `data_frame` function.
```{r}
grades <- data_frame(names = c("John", "Juan", "Jean", "Yao"), exam_1 = c(95, 80, 90, 85), exam_2 = c(90, 85, 85, 90))
grades
```

Note that base R (without packages loaded) has a function with a very similar name, `data.frame`, that can be used to create a regular data frame rather than a tibble. One other important difference is that by default `data.frame` coerces characters into factors without providing a warning or message:
```{r}
grades <- data.frame(names = c("John", "Juan", "Jean", "Yao"), exam_1 = c(95, 80, 90, 85), exam_2 = c(90, 85, 85, 90))

class(grades$names)
```

To avoid this, we use the rather cumbersome argument `stringsAsFactors`:
```{r}
grades <- data.frame(names = c("John", "Juan", "Jean", "Yao"), exam_1 = c(95, 80, 90, 85), exam_2 = c(90, 85, 85, 90),
stringsAsFactors = FALSE)
class(grades$names)
```

To convert a regular data frame to a tibble, you can use the as_tibble function.
```{r}
as_tibble(grades) %>% class()
```




# 5.11 The dot operator

One of the advantages of using the pipe `%>%` is that we do not have to keep naming new objects as we manipulate the data frame. As quick reminder, if we want to compute the median murder rate for states in the southern states, instead of typing:
```{r}
tab_1 <- filter(murders, region == "South")
tab_2 <- mutate(tab_1, rate = total / population * 10^5)
rates <- tab_2$rate
median(rates)
```

We can avoid defining any new intermediate objects by instead typing:
```{r}
filter(murders, region == "South") %>% 
  mutate(rate = total / population * 10^5) %>% 
  summarize(median = median(rate)) %>%
  pull(median)
```

We can do this because each of these functions takes a data frame as the first argument. But what if we want to access a component of the data frame. For example, what if the `pull` function was not available and we wanted to access `tab_2$rate`? What data frame name would we use? The answer is the **dot operator**.

For example to access the rate vector without the `pull` function we could use
```{r}
rates <-filter(murders, region == "South") %>% 
  mutate(rate = total / population * 10^5) %>% 
  .$rate
median(rates)
```

In the next section, we will see other instances in which using the `.` is useful.



# 5.12 `do`
**tidyersd 외의 function(like quantile)는 grouped tibbles를 처리하는 법을 모르며, dataframe을 도출하지도 않는다:sol) `do`사용**

**`do`: `tidyverse %>% do(function(.))`**
**do의 도출값 tibble은 '.'으로 표현됨. 따라서 function의 입력값으로 '.'을 써준다. tidyverse와 Rfunction간 bridge**
`do`:

The tidyverse functions know how to interpret grouped tibbles. Furthermore, to facilitate stringing commands through the pipe `%>%`, tidyverse functions consistently return data frames, since this assures that the output of a function is accepted as the input of another. 
But most R functions do not recognize grouped tibbles nor do they return data frames. 
The `quantile` function is an example we described in Section 5.7.1. The `do` functions serves as a bridge between R functions such as `quantile` and the tidyverse. The `do` function understands grouped tibbles and always returns a data frame.

In Section 5.7.1, we noted that if we attempt to use `quantile` to obtain the min, median and max in one call, we will receive an error: 
`Error: expecting result of length one, got : 2.`
```{r}
data(heights)
heights %>% 
  filter(sex == "Female") %>%
  summarize(range = quantile(height, c(0, 0.5, 1)))
```

We can use the `do` function fix this.

First we have to write a function that fits into the tidyverse approach: that is, it receives a data frame and returns a data frame.
```{r}
my_summary <- function(dat){
  x <- quantile(dat$height, c(0, 0.5, 1))
  data_frame(min = x[1], median = x[2], max = x[3])
}
```

We can now apply the function to the heights dataset to obtain the summaries:
```{r}
heights %>% 
  group_by(sex) %>% 
  my_summary
```

But this is not what we want. We want a summary for each sex and the code returned just one summary. This is because `my_summary` is not part of the tidyverse and does not know how to handled grouped tibbles. `do` makes this connection:
```{r}
heights %>% 
  group_by(sex) %>% 
  do(my_summary(.))
```

Note that here we need to use the dot operator. The tibble created by `group_by` is piped to `do`. Within the call to `do`, the name of this tibble is `.` and we want to send it to my_summary`. If you do not use the dot, then `my_summary` has __no argument and returns an error telling us that `argument "dat"` is missing. You can see the error by typing:
```{r}
heights %>% 
  group_by(sex) %>% 
  do(my_summary())
```

If you do not use the parenthesis, then the function is not executed and instead do tries to return the function. This gives an error because do must always return a data frame. You can see the error by typing:
```{r}
heights %>% 
  group_by(sex) %>% 
  do(my_summary)
```



# 5.13 The purrr package

**functions which 같은 function을 한 vector의 모든 element에 반복적용: `sapply`**
**sapply는 출력값의 data type을 통제하지 못한다:sol) purrr package의 `map` 사용**
map: list 도출
map_dbl : numeric 도출
map_df : **tibble data frame**도출
c.f)단, function의 도출형태가 list or vector with name이어야됨
:sol)function의 마지막 줄(도출값)에 data_frame() function 적용



In Section 4.5 we learned about the `sapply` function, which permitted us to apply the same function to each element of a vector. We constructed this function:
```{r}
compute_s_n <- function(n){
  x <- 1:n
  sum(x)
}
```

and used `sapply` to compute the sum of the first `n` integers for several values of `n` like this:
```{r}
n <- 1:25
s_n <- sapply(n, compute_s_n)
```

This type of operation, applying the same function or procedure to elements of an object, is quite common in data analysis. 
The **purrr** package includes functions similar to `sapply` but that better interact with other tidyverse functions. The main advantage is that we can better control the output type of functions. 

In contrast, `sapply` can return several different object types; for example, we might expect a numeric result from a line of code, but `sapply` might convert our result to character under some circumstances. 
**purrr** functions will never do this: they will return objects of a specified type or return an error if this is not possible.


The first purrr function we will learn is `map`, which works very similar to `sapply` but always, without exception, returns a list:
```{r}
library(purrr)
s_n <- map(n, compute_s_n)
class(s_n)
```

If we want a numeric vector, we can instead use `map_dbl` which always returns a vector of numeric values.
```{r}
s_n <- map_dbl(n, compute_s_n)
class(s_n)
```
This produces the same results as the `sapply` call shown above.

A particularly useful **purrr** function for interacting with the rest of the tidyverse is `map_df`, which always returns a _tibble data frame_. 
However, the function being called needs to return a vector a or list with names. For this reason, the following code would result in a `Argument 1 must have names` error:
```{r}
s_n <- map_df(n, compute_s_n)
```
We need to change the function to make this work:
```{r}
compute_s_n <- function(n){
  x <- 1:n
  data_frame(sum = sum(x))
}
s_n <- map_df(n, compute_s_n)
head(s_n)
```


# 5.14 Tidyverse conditionals

A typical data analysis will often involve one or more conditional operation. In Section 4.1 we described the `ifelse` function, which we will use extensively in this book. 
In this section we present two **dplyr** functions that provide further functionality for performing conditional operations.

#### 5.14.1 `case_when`
**`case_when`:ifelse와 비슷, 조건이 굉장히 많을 때 사용하면 유리**
**`case_when(조건문1 ~ 도출값1, 조건문2 ~ 도출값2, .... TRUE ~ 도출값n)`**

The `case_when` function is useful for vectorizing conditional statements. 
It is similar to `ifelse` but can output any number of values, as opposed to just `TRUE` or `FALSE`. Here is an example splitting numbers into negative, positives and 0:
```{r}
x <- c(-2, -1, 0, 1, 2)
case_when(x < 0 ~ "Negative", x > 0 ~ "Positive", TRUE ~ "Zero")
```

A common use for this function is to define categorical variables based on existing variables. For example, suppose we we want compare the murder rates in in three groups of states: _New England_, _West Coast_, _South_, and _other_. For each state, we need to ask if it is in _New England_, if it is not we ask if it is in the _West Coast_, if not we ask if it is in the _South_ and if not we assign _other_. Here is how we use `case_when` to do this:
```{r}
data(murders)
murders %>% 
  mutate(group = case_when(
    abb %in% c("ME", "NH", "VT", "MA", "RI", "CT") ~ "New England",
    abb %in% c("WA", "OR", "CA") ~ "West Coast",
    region == "South" ~ "South",
    TRUE ~ "other")) %>%
  group_by(group) %>%
  summarize(rate = sum(total) / sum(population) * 10^5) %>%
  arrange(rate)
```


#### 5.14.2 `between`
**`between`:특정 벡터값이 특정 범위 사이에 있는지**
**:`between(x, a, b)`**
**x:벡터, 범위: a<, <b**

A common operation in data analysis is to determine if a value falls inside an interval. We can check this using conditionals. 
For example to check if the elements of a vector `x` are between `a` and `b` we can type
```{r}
x >= a & x <= b
```

However, this can become cumbersome, especially within the tidyverse approach. The between function performs the same operation.
```{r}
between(x, a, b)
```




# 5.15 Exercises

1. Load the murders dataset. Which of the following is true?
```{r}
data("murders")
murders
class(murders)
#tidy&data.frame
#B
```

2. Use `as_tibble` to covert the `murders` data table into a tibble and save it in an object called `murders_tibble`.
```{r}
murders_tibble <- as_tibble(murders)
```
 
3.Use the `group_by` function to convert murders into a tibble that is grouped by region.
```{r}
c <- group_by(murders, region)
class(c)
```

4. Write tidyverse code that is equivalent to this code: `exp(mean(log(murders$population)))`. Write it using the pipe so that each function is called without arguments. Use the dot operator to access the population. Hint: The code should start with `murders %>%`..
```{r}
?exp
murders %>% select(population) %>% log() %>% summarize(average = mean(population)) %>% exp()
##summarize를 거치지 않고 바로 mean을 하지 numeric이 아니라고 error가 났다. 이것에서 summarize는 data.frame등의 복잡한 argument에 대한 하나의 summary statistic을 계산하는데 유용하다는 점을 알 수 있다.
```


5. Use the `map_df` to create a data frame with three columns named `n`, `s_n`, and `s_n_2`. 
The first column should contain the numbers 1 through 100. The second and third columns should each contain the sum of 1 through  n with n the row number..
```{r}
my_function <- function(n){
  x <- 1:n
  data_frame(sum=sum(x))
}
n<-1:100
s_n <- map_df(n, my_function)
my_function_2 <- function(n){
  x <- s_n$sum[1:n]
data_frame(sum=sum(x))
}
my_function_2(1)
s_n_2 <- map_df(n, my_function_2)
s_n_2
data_frame(n, s_n=s_n$sum[n], s_n_2=s_n_2$sum[n])
```

please save...
error...