---
title: "R Notebook"
output: html_notebook
---
# Chapter 5 The tidyverse
`tidy`:data의 한 종류
`tidyverse` : package, tidy 이용에 유리
 
We can load all the tidyverse packages at once by installing and loading the `tidyverse` package:
```{r}
install.packages("tidyverse")
install.packages("dslabs")
library(tidyverse)
```

in `tidyverse`: 'dplyr', 'purrr', and 'ggplot2' packages.



#### 5.1 Tidy data
We say that a data table is in `tidy` format if each row represents one observation and columns represent the different variables available for each of these observations. 
`tidy` : row(행,가로) : one obsevation
         column(열) : different variables
         
The `murders` dataset is an example of a tidy data frame.
```{r}
library(dslabs)
murders
```
Each row represent a state with each of the five columns providing a different variable related to these states: name, abbreviation, region, population, and total murders.

To see how the same information can be provided in different formats, consider the following example:
```{r}
#>        country year fertility
#> 1      Germany 1960      2.41
#> 2  South Korea 1960      6.16
#> 3      Germany 1961      2.44
#> 4  South Korea 1961      5.99
#> 5      Germany 1962      2.47
#> 6  South Korea 1962      5.79
#> 7      Germany 1963      2.49
#> 8  South Korea 1963      5.57
#> 9      Germany 1964      2.49
#> 10 South Korea 1964      5.36
#> 11     Germany 1965      2.48
#> 12 South Korea 1965      5.16
```
This is a tidy dataset because each row presents one observation with the three variables being county, year and fertility rate.

Originally, the data was in the following format:
```{r}
#>       country 1960 1961 1962 1963 1964 1965
#> 1     Germany 2.41 2.44 2.47 2.49 2.49 2.48
#> 2 South Korea 6.16 5.99 5.79 5.57 5.36 5.16
```
This is not tidy format.
1. each row include several observations.
2. the same variable, year is stored in the header.

For the tidyverse packages to be optimally used, data need to be reshaped into `tidy` format.
`tidyverse`package 사용을 위해선 `tidy`format이어야함.




# 5.2 Exercises
1. Examine the built-in dataset `co2`. Which of the following is true:
```{r}
co2
#row에 여러개의 observation이 있다 > tidy data 가 아니다.
class(co2)
#C
```

2. Examine the built-in dataset `ChickWeight`. Which of the following is true:
```{r}
ChickWeight
class(ChickWeight)
#D
```
3. Examine the built-in dataset BOD. Which of the following is true:
```{r}
BOD
#C
```
4. Which of the following built-in datasets is tidy (you can pick more than one):
```{r}
BJsales
EuStockMarkets
DNase
Formaldehyde
Orange
UCBAdmissions
#B,C,D,E
```



# 5.3 Manipulating data frames
The `dplyr` package from the `tidyverse`
:to change the data table by adding a new column, we use `mutate`.
To filter the data table to a subset of rows, we use `filter`. 
Finally, to subset the data by selecting specific columns, we use `select`.

#### 5.3.1 Adding a column with `mutate`
**The function `mutate` takes the data frame as a first argument and the name and values of the variable as a second argument using the convention `name = values`.**

So, to add murder rates, we use:
```{r}
library(dslabs)
data("murders")
murders <- mutate(murders, rate = total / population*100000)
```
*dplyr 에서는 first argument의 data frame variable은 자동으로 인식함
*원 `murders` data frame은 그대로이므로 `date(murders)`를 다시 실행하면 original data frame 실행

We can see that the new column is added:
```{r}
head(murders)
```


#### 5.3.2 Subsetting with `filter`
Now suppose that we want to filter the data table to only show the entries for which the murder rate is lower than 0.71. **To do this we use the filter function, which takes the data table as the first argument and then the conditional statement as the second.**
* `!=` : remove row
 ex) filter(murders, state! = "Florida")
     >Florida 제외 state들만 표시
```{r}
filter(murders, rate <= 0.71)
```


#### 5.3.3 Selecting columns with `select`
If we want to view just a few, we can use the **dplyr** `select` function.
```{r}
new_table <- select(murders, state, region, rate)
filter(new_table, rate <= 0.71)
```
In the call to `select`, the first argument `murders` is an object, but `state`, `region`, and `rate` are variable names.



# 5.4 Exercises
1. Load the dplyr package and the murders dataset.
```{r}
library(dplyr)
library(dslabs)
data(murders)
```
You can add columns using the **dplyr** function `mutate`. This function is aware of the column names and inside the function you can call them unquoted:
```{r}
murders <- mutate(murders, population_in_millions = population / 10^6)
```
We can write `population` rather than `murders$population`. The function `mutate` knows we are grabbing columns from `murders`.

Use the function `mutate` to add a murders column named `rate` with the per 100,000 murder rate as in the example code above. Make sure you redefine `murders` as done in the example code above ( murders <- [your code]) so we can keep using this variable.
```{r}
murders <- mutate(murders, rate = total / population * 100000)
murders
```

2. If `rank(x)` gives you the ranks of x from lowest to highest, `rank(-x)` gives you the ranks from highest to lowest. Use the function `mutate` to add a column rank containing the `rank`, from highest to lowest murder rate. Make sure you redefine `murders` so we can keep using this variable.
```{r}
murders <- mutate(murders, rank=rank(-rate))
murders
```

3. With **dplyr**, we can use `select` to show only certain columns. For example, with this code we would only show the states and population sizes:
```{r}
select(murders, state, population) %>% head()
```
Use `select` to show the state names and abbreviations in `murders`. Do not redefine `murders`, just show the results.
```{r}
select(murders, state, abb)
```

4. The **dplyr** function `filter` is used to choose specific rows of the data frame to keep. Unlike `select` which is for columns, `filter` is for rows. For example, you can show just the New York row like this:
```{r}
filter(murders, state == "New York")
```
You can use other logical vectors to filter rows.

Use `filter` to show the top 5 states with the highest murder rates. After we add murder rate and rank, do not change the murders dataset, just show the result. Remember that you can filter based on the `rank` column.
```{r}
filter(murders, rank <= 5)
```

5. We can remove rows using the `!=` operator. For example, to remove Florida, we would do this:
```{r}
no_florida <- filter(murders, state != "Florida")
```
Create a new data frame called `no_south` that removes states from the South region. How many states are in this category? You can use the function `nrow` for this.
**nrow : row의 수를 측정하는 function**
```{r}
no_south <- filter(murders, region != "South")
nrow(no_south)
#34
```

6. We can also use `%in%` to filter with **dplyr**. You can therefore see the data from New York and Texas like this:
```{r}
filter(murders, state %in% c("New York", "Texas"))
```
Create a new data frame called `murders_nw` with only the states from the Northeast and the West. How many states are in this category?
```{r}
murders_nw <- filter(murders, region %in% c("Northeast", "West"))
nrow(murders_nw)
#22
```

7. Suppose you want to live in the Northeast or West and want the murder rate to be less than 1. We want to see the data for the states satisfying these options. Note that you can use logical operators with `filter`. Here is an example in which we filter to keep only small states in the Northeast region.
```{r}
filter(murders, population < 5000000 & region == "Northeast")
```
Make sure `murders` has been defined with `rate` and `rank` and still has all states. Create a table called `my_states` that contains rows for states satisfying both the conditions: it is in the Northeast or West and the murder rate is less than 1. Use `select` to show only the state name, the rate and the rank.
```{r}
my_states <- filter(murders, region %in% c("Northeast", "West") & rate < 1)
select(my_states, state, rate, rank)
```

# 5.5 The pipe: `%>%`
With **dplyr** we can perform a series of operations, for example `select` and then `filter`, by sending the results of one function to another using what is called the pipe operator: `%>%`.
**`%>%` : dplyr 안에서 operation 여러개를 동시진행(왼쪽의 결과를 오른쪽 function의 first argument로 처리)**
**intermediate object 발생x**

**original data → select → filter** 
 

For such an operation, we can use the pipe %>%. The code looks like this:
```{r}
murders %>% select(state, region, rate) %>% filter(rate <= 0.71)
```

In general, the pipe sends the result of the left side of the pipe to be the first argument of the function on the right side of the pipe. Here is a very simple example:
```{r}
16 %>% sqrt()
```

We can continue to pipe values along:
```{r}
16 %>% sqrt() %>% log2()
```
The above statement is equivalent to `log2(sqrt(16))`.

Remember that the pipe sends values to the first argument, so we can define other arguments as if the first argument is already defined:
```{r}
16 %>% sqrt() %>% log(base = 2)
```
Therefore, when using the pipe with data frames and **dplyr**, we no longer need to specify the required first argument since the **dplyr** functions we have described all take the data as the first argument. In the code we wrote:
```{r}
murders %>% select(state, region, rate) %>% filter(rate <= 0.71)
```
`murders` is the first argument of the `select` function, and the new data frame (formerly `new_table`) is the first argument of the `filter` function.

Note that the pipe works well with functions where the first argument is the input data. Functions in **tidyverse** packages like **dplyr** have this format and can be used easily with the pipe.



# 5.6 Exercises

1. The pipe `%>%` can be used to perform operations sequentially without having to define intermediate objects. Start by redefining murder to include rate and rank.
```{r}
murders <- mutate(murders, rate =  total / population * 100000, rank = rank(-rate))
```
In the solution to the previous exercise, we did the following:
```{r}
my_states <- filter(murders, region %in% c("Northeast", "West") & rate < 1)

select(my_states, state, rate, rank)
```
The pipe `%>%` permits us to perform both operations sequentially without having to define an intermediate variable `my_states`. We therefore could have mutated and selected in the same line like this:
```{r}
mutate(murders, rate =  total / population * 100000, rank = rank(-rate)) %>%
  select(state, rate, rank)
```
Notice that `select` no longer has a data frame as the first argument. The first argument is assumed to be the result of the operation conducted right before the %>%.

Repeat the previous exercise, but now instead of creating a new object, show the result and only include the state, rate, and rank columns. Use a pipe `%>%` to do this in just one line.
```{r}
filter(murders, region %in% c("Northeast", "West") & rate < 1) %>% select(state, rate, rank)
```

2. Reset `murders` to the original table by using `data(murders)`. Use a pipe to create a new data frame called `my_states` that considers only states in the Northeast or West which have a murder rate lower than 1, and contains only the state, rate and rank columns. The pipe should also have four components separated by three `%>%`. The code should look something like this:
```{r}
data(murders)
my_states <- murders %>% mutate(rate = total / population * 100000, rank = rank(-rate)) %>% filter(region %in% c("Northeast", "West") & rate < 1 ) %>% select(state, rate, rank)
my_states
#**Northeast or West이므로 `==`이 아니라 `%in%을 쓴다**
```



# 5.7 Summarizing data
we cover two new **dplyr** verbs that make these computations easier: 
`summarize` and `group_by`. We learn to access resulting values using the `pull` function.


# 5.7.1 `summarize`
